%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://osam.me/}{\Large Ousmane Amadou}} & Email : \href{mailto:ousmane.amadou89@gmail.com}{ousmane.amadou89@gmail.com}\\
  \href{http://osam.model/}{http://osam.me} & Mobile : +1-88847-571-7353 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Of Toronto}{Toronto, ON}
      {Bachelor of Science in Computational Cognitive Science and Statistics}{Sept 2017 -- Present}
      \resumeItemListStart
        \resumeItem{Relevant Courses}
          {Introduction to Theory of Computation, Data Computation and The Mind, Software Design, Interaction Design, Modern Symbolic Logic, Linear Algebra I, Calculus I and II}
        \resumeItem{Activities}
          {Phi Kappa Sigma, Game Development Club, Vocomotive Jazz Choir, The Entrepreneurship Hatchery}
      \resumeItemListEnd
    \resumeSubheading
      {Earl of March Secondary School}{Ottawa, ON}
      {Ontario Secondary School Diploma}{Sept 2012 -- June 2016}
      \resumeItemListStart
        \resumeItem{Activities}
          {President of Computer Science Club, Musical Theatre Pit Band, Jazz Band}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Weav}{Scarborough, ON}
      {Technical Co-Founder and Developer}{Sept 2017 - May 2018}
      \resumeItemListStart
        \resumeItem{Project Summary}
          {Weav is an app that matches drivers and riders for scheduled rideshares. Please visit https:/letsweav.com for more.}
        \resumeItem{Milestones}
          {Successfully completed 20,000 dollars in seed round funding and admitted as a member of the Hatchery's 2018 Summer Nest Cohort. }
        \resumeItem{Technical Writing}
          {Assumed all of the technical writing and data archival duties. Created and maintained 
          back-end API documentation, uml diagrams, and system design documents.}
        \resumeItem{System Architecture}
          {Designed the core system architecture, using AWS as our primary cloud service provider.}
        \resumeItem{Development}
          {Developed and deployed the first two versions of the company website from reference Photoshop files to an AWS ECS Instance.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Computer Science Enrichment Club}{Scarborough, ON}
      {Sessional Lecturer}{Sep 2017 - Apr 2018}
      \resumeItemListStart
        \resumeItem{Algorithm Lectures}
        {Presented a series of bi-weekly competitive progamming lectures to a group of keen rst year computer
        science students. Topics that I covered were basic data structures, graph data strucutures, and dynamic programming problems.
        See the presentation slides \href{https://github.com/csecutsc/T-414-AFLV}{here.} }
      \resumeItemListEnd

    \resumeSubheading
      {Ottawa-Carleton District School Board}{Ottawa, ON}
      {On Call Sound/Lighting Board Operator}{Sept 2013 - Jul 2016}
      \resumeItemListStart
        \resumeItem{Liason}
          {Elected A/V Liason for the EOM students council for a 1 year term and collaborated 
            with event organizers to design sound and lighting for coffee houses, dance showcases, 
            etc. }
        \resumeItem{Sound Team Member}
          {Mixed audio and managed sound cues for live events. Trained new members to understand basic cable management, setting up microphones, 
          using a mixer, etc..}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Shoppr}
      {A smart shopping tool for mall and indoor shopping environments. See more
       \href{https://docs.google.com/presentation/d/19Re0_eoscr-ljDUIEc389gzJJyxJQ8Loe7jXswiwRM8/edit?usp=sharing}{here.}}
    \resumeSubItem{Solutions Archive}
      {A snapshot archive of my solutions to programming competitions. These solutions were written in C++, Java or Python. \href{https://github.com/ousmane-amadou/competitive-programming}{Go to github.}}
    \resumeSubItem{Text Time}
      {A speed texting prototyped at UofTHacksV. Made in Unity3D+C\#. \href{https://github.com/ousmane-amadou/competitive-programming}{Go to github.} }
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Scripting}
      {HTML, CSS, Javascript, Bootstrap, SemanticUI}
    \resumeSubItem{Programming}
      {Python, Java, C++, C\#, \LaTeX}
    \resumeSubItem{Technologies}
      {AWS, Trello, Unity3D, Adobe XD, Adobe Photoshop}
    \resumeSubItem{Other}
      {UX Design, Technical Writing, Sound Mixing}
 \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Awards and Achievments}
\resumeSubHeadingListStart
    \resumeSubItem{ACM-ICPC Regional Qualifier}
      {Placed 28th out of 126 teams at the 2016 ACM-ICPC regional qualifier.}
    \resumeSubItem{Ottawa Youth Network's App Jam}
      {Finalist out of 100+ Submissions.}
    \resumeSubItem{UTSC's The Hub Pitch Competition}
      {Winner of 2017's Pitch Competition for Weav.}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
