\documentclass[twoside]{article}
\setlength{\oddsidemargin}{0.25 in}
\setlength{\evensidemargin}{-0.25 in}
\setlength{\topmargin}{-0.6 in}
\setlength{\textwidth}{6.5 in}
\setlength{\textheight}{8.5 in}
\setlength{\headsep}{0.75 in}
\setlength{\parindent}{0 in}
\setlength{\parskip}{0.1 in}

%
% ADD PACKAGES here:
%

\usepackage{amsmath,amsfonts,amssymb,graphicx,mathtools,flexisym}

%
% The following commands set up the lecnum (lecture number)
% counter and make various numbering schemes work relative
% to the lecture number.
%
\newcounter{lecnum}
\renewcommand{\thepage}{\thelecnum-\arabic{page}}
\renewcommand{\thesection}{\thelecnum.\arabic{section}}
\renewcommand{\theequation}{\thelecnum.\arabic{equation}}
\renewcommand{\thefigure}{\thelecnum.\arabic{figure}}
\renewcommand{\thetable}{\thelecnum.\arabic{table}}

%
% The following macro is used to generate the header.
%
\newcommand{\lecture}[4]{
   \pagestyle{myheadings}
   \thispagestyle{plain}
   \newpage
   \setcounter{lecnum}{#1}
   \setcounter{page}{1}
   \noindent
   \begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    \hbox to 6.28in { {\bf COG250H1: Introduction to Cognitive Science
	\hfill Fall 2018} }
       \vspace{4mm}
       \hbox to 6.28in { {\Large \hfill Lecture #1: #2  \hfill} }
       \vspace{2mm}
       \hbox to 6.28in { {\it Lecturer: #3 \hfill Scribes: #4} }
      \vspace{2mm}}
   }
   \end{center}
   \markboth{Lecture #1: #2}{Lecture #1: #2}

   {\bf Note}: {\it LaTeX template courtesy of UC Berkeley EECS dept.}

   {\bf Disclaimer}: {\it These notes have not been subjected to the
   usual scrutiny reserved for formal publications.  They may be distributed
   outside this class only with the permission of the Instructor.}
   \vspace*{4mm}
}
%
% Convention for citations is authors' initials followed by the year.
% For example, to cite a paper by Leighton and Maggs you would type
% \cite{LM89}, and to cite a paper by Strassen you would type \cite{S69}.
% (To avoid bibliography problems, for now we redefine the \cite command.)
% Also commands that create a suitable format for the reference list.
\renewcommand{\cite}[1]{[#1]}
\def\beginrefs{\begin{list}%
        {[\arabic{equation}]}{\usecounter{equation}
         \setlength{\leftmargin}{2.0truecm}\setlength{\labelsep}{0.4truecm}%
         \setlength{\labelwidth}{1.6truecm}}}
\def\endrefs{\end{list}}
\def\bibentry#1{\item[\hbox{[#1]}]}

%Use this command for a figure; it puts a figure in wherever you want it.
%usage: \fig{NUMBER}{SPACE-IN-INCHES}{CAPTION}
\newcommand{\fig}[3]{
			\vspace{#2}
			\begin{center}
			Figure \thelecnum.#1:~#3
			\end{center}
	}
% Use these for theorems, lemmas, proofs, etc.
\newtheorem{theorem}{Theorem}[lecnum]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newenvironment{proof}{{\bf Proof:}}{\hfill\rule{2mm}{2mm}}

% **** IF YOU WANT TO DEFINE ADDITIONAL MACROS FOR YOURSELF, PUT THEM HERE:

\newcommand\E{\mathbb{E}}

\begin{document}
%FILL IN THE RIGHT INFO.
%\lecture{**LECTURE-NUMBER**}{**DATE**}{**LECTURER**}{**SCRIBE**}
\lecture{2}{Categorization (Part 1)}{Anderson Todd}{Ousmane Amadou}
%\footnotetext{These notes are partially based on those of Nigel Mansell.}

% **** YOUR NOTES GO HERE:
\section{An Overview of Cognitive Science (CogSci)}
\subsection{Motivation}
Key writing points:
  (1) Black box approach
  (2) Examples of cogsci in real life (Machine learning, Stock Crash, )
  (3) Literacy
As machine learning is picking up (quickly), also hitting a problem that many of these problems are "black boxes"
(not understanding how it actually works, or how it works under the hood)

\subsection{Theoretical Constucts and Plausibility}
Key writing points:
  (1) Metaphors and multi aptness
  (2) Convergence of evidence (works for multiple streams of evidence)
      example:

\subsection{What is CogSci?}
We don't know what makes us think.

The one thing we can't account for in our scientific explanations is
how we produce scientific explanations.

Cogsci seeks to develop a common language for describing \textbf{cognitive phenomena}
that can be understood through multiple disciplines.

There are three models of cognitive science:
\begin{enumerate}
  \item Generic Nominalism
    \begin{itemize}
      \item The weakest definition of CogSci
      \item In this vision, CogSci is not it's own discipline. Instead, it is
            a generic term describing the study of mind in CogSci's subdisciplines.
      \item This vision is generally not accepted in third generation cognitive science
    \end{itemize}
  \item Interdisciplinary Ecclecticsm
  \begin{itemize}
    \item A stonger definition than generic nominalism, not the strongest
    \item This approach is characterized by drawing from CogSci's sub disciplines
          to analyze the mind. Instead of holding to a single paradigm or framework
          of thought, IE seeks to integrate knowledge from all the sub disciplines to
          gain insight into the mind.
    \item Analogy: Interfaith dialgoue
    \item This model, however, is very unstable. Typically this model either devolves
          into generic nominalism or evolves into synoptic integration.
  \end{itemize}
  \item Synoptic Integration
  \begin{itemize}
    \item The strongest definition of CogSci.
    \item CogSci, under this model, is a unique discipline. Doing CogSci is deliberate.
  \end{itemize}
\end{enumerate}

% So far we have made the following assumptions:
% \begin{enumerate}
% \item The LP is in the standard form i.e.\\
% \begin{eqnarray*}
% \min c^T x  \\
% \mbox{s.t}\  Ax=b,
% \newline
% \\x\geq 0
% \end{eqnarray*}
% \\
% where $C,x\in{\mathbb R^{n}}$, $A \in {\mathbb R^{m\times n}} $ , $b \in{\mathbb R^{m}}$ and $rank(A)= m$
%
% \item Every Basic Feasible Solution i.e. BFS is non-degenerate
% \item BFS is in the form
% \begin{equation}
% [I \mid Y] \left[ \begin{matrix}
% x
% \end{matrix}\right] = y_0
% \label{eq1}
% \end{equation}
% where I is $m \times m$ Identity Matrix,
% $ x = \left[ \begin{array}{cc}
% x_{B}  \\
% x_{NB}   \end{array} \right]$,~~$x_B \in R^n $ and $x_{NB} \in R^{n-m}$
%
% \end{enumerate}
\section{Naturalistic Imperative}
It is our desire to bring our minds in line with all the scientific
disciplines.

The goal of science is to 'naturalize' our understanding of the universe.

The Naturalistic Imperative is a term coined by John Vervaeke. To understand
the naturalistic imperative it is useful to look at previous scientific revolutions:

\subsection{Analyze}
Talking points:
Introduction to the Presocratics: https://www.youtube.com/watch?v=ZkMAx04jDx0
Myth vs. Reason
(1) Presocratic philosophers
  (0) Why study them?
    (i) They are the intellectual and cultural foundations of western civilization
        If one wants to understand western civilization one must understand Plato
        and Aristotle.. If one is to understand Plato and Aristotle, one would
        benefit from understanding the pre socratics.
    (ii) Presocratics birthed rational thought... It is here that the logos
        came about... The fact that rational thought came from here
  (1) Not actually philosophers, wouldn't call themselves philosophers either..
      A better way to describe these group of ople would be thinkers
  (2) End of Presocratic era: The nature of philosophy changed from studying
  nature to .. Socrates stopped focusing on metaphysical questions, becuase
  he felt that studying those questions had no impact on his life. Instead, he started
  turned his attention to practical morality and political thought.

Ancient Greece - Presocratic philosophers

Thales
Not much left on him
We know three things

\subsection{Formalize}

\subsection{Mechanize}


\begin{itemize}
\item Generic step of the algorithm is to swap a basic variable with a non basic variable. For now assume
that we have selected basic variable $x_p$ and non-basic variable $x_q$ to swap
\item $x_p$ can be swapped with $x_q$ if and only if $Y_{pq} \ne 0$ because if $Y_{pq}$ is equal to 0 then column vector $Y_q$
can be represented as linear combination of m − 1 basis vectors i.e.
\[ Y_q=\sum_{i=1~i \neq p}^m y_{iq} \ast I_i\]
and hence $Y_q$ cannot be included in basic solution
\item Now make $q^{th}$ column as $ \left[ \begin{array}{ccccccc}
 0 & ... & 0 & 1_p & 0 & ... & 0
  \end{array} \right]$ where $1_p$
  signifies 1 at
  $p^{th}$
  position. For that

 divide$p_{th}$row of matrix$ \left[ \begin{array}{cc}
I &
Y  \end{array} \right]$
and matrix $ \left[ \begin{array}{cc}
Y(0) \end{array} \right]$
by
$Y_{pq}$ and apply the row operation $R_i \Rightarrow R_i - Y_{iq} \ast R_p$
\end{itemize}
\section{Determining the Leaving Variable p}
\begin{itemize}
\item While applying row transformation of
$ \left[ \begin{array}{cc}
I &
Y  \end{array} \right]$ rows of $ \left[ \begin{array}{c}
I  \end{array} \right]$ also changes and are given by
\[Y_{i0}\textprime =Y_{i0}-Y_{iq}\ast Y_{p0} / Y_{i0} \]
Condition $Y_{i0}\textprime \ge 0 $ must satisfy otherwise $x_q$ would not be a BFS.
\item So choose p such that
\[p \in S = \underset{i}{\operatorname{argmin}} \{Y_{i0}/Y_{iq} | Y_{iq} \ge 0\}\]
\item If number of elements in S is $>$ 1 then the would become degenerate. Since non-degeneracy is assumed
\[p = \underset{i}{\operatorname{argmin}}\{Y_{i0}/Y_{iq} | Y_{iq} \ge 0\}\]
\end{itemize}

\section{Determining the Entering Variable q}
\begin{itemize}
\item We Know that
\[ \left[ \begin{array}{cc}
I &
Y  \end{array} \right] \left[ \begin{array}{cc}
x_B \\
x_{NB}  \end{array} \right]= \left[ \begin{array}{c}

Y(0)  \end{array} \right] \]
\[ x_B=Y_0-Yx_{NB} \]
\[Where \left[ \begin{array}{cc}
x_B \\
x_{NB}  \end{array} \right] \ge 0 \]
\item Initial Cost:
\[c^T\left[ \begin{array}{cc}
x_B \\
x_{NB}  \end{array} \right] =c_B^Tx_B+c_{NB}^Tx_{NB} \]
\[=c_B^Tx_B\]
\[=c_B^T Y_0\]
\[since~~x_{NB}=0 ~~and~~ I \ast x_B + Y \ast x_{NB}= Y_0\]
\item Now cost is
\[c^T\left[ \begin{array}{cc}
x_B \\
x_{NB}  \end{array} \right] =c_B^Tx_B+c_{NB}^Tx_{NB} \]
\[=c_B^T(Y_0-Yx_{NB})+c_{NB}^Tx_{NB}\]
\[ =c_B^TY_0+(c_{NB-Y^Tc_B})^Tx_{NB} \]
\item Now we can choose q such for which	$(c_{NB}-Y^Tc_B)_q<0$
\item Formalizing the above concept
\[ \left[ \begin{array}{cccccccc}
1 & 0 & ... & 0 & Y_{1,m+1} &Y_{1,m+2} & ... & Y_{1,n} \\
0 & 1 & ... & 0 & Y_{2,m+1} &Y_{2,m+2} & ... & Y_{2,n} \\
. & . & . & . & . & . & ... & . \\
. & . & . & . & . & . & ... & . \\
. & . & . & . & . & . & ... & . \\
0 & 0 & ... & 1 & Y_{m,m+1} &Y_{m,m+2} & ... & Y_{m,n} \\
  \end{array} \right] \left[ \begin{array}{c}
x_1\\ .\\ .\\ .\\ x_m\\ .\\ .\\ .\\x_n   \end{array} \right] = \left[ \begin{array}{c}
y_{10}\\ .\\ .\\ .\\ y_{m0}\\ .\\ .\\ .\\y_{n0}   \end{array} \right]  \]
and
\[(c_{NB}-Y^Tc_B)^Tx_{NB}=\sum_{j=m+1}^n(c_j-Z_j)\ast x_j\]
\[Where ~~ Z_j=\sum_{i=1}^m(Y_{i,j}\ast c_i)\]
\item To determine the entering variable choose j such that $(c_j - Z_j ) < 0$
\end{itemize}
\subsection{Theorem 8.1.} Given a non-degenerate Basic Feasible Solution with objective value $Z\textprime$ . Suppose $c_j - Z_j\textprime < 0$
for some j there is a feasible solution with objective value $< Z\textprime$ . Also if variable $x_j$ can be substituted for
a variable in the basis for a new BFS, we get new BFS with value $Z_0 < 0$. If this cannot be done then the
solution is unbounded.
\section{Optimality condition}
The Basic Feasible Solution is optimal if
\[\forall,~~~~ c_j - 	Z_j \ge 0\]
\section{Some Points to Ponder}
\begin{itemize}
\item f there does not exist p to replace then we have founded the recession direction and the cost can be
reduced to $-\infty$
\item In the worst case the Simplex Algorithm might visit all the extreme points. Example - Klee Minty cube
\end{itemize}
\pagebreak
\section{Duality}
Every linear programming problem, referred to as a primal problem, can be converted into a dual problem,
which provides an upper bound to the optimal value of the primal problem. The primal problem is:
\[\underset{x}{\operatorname{min}} ~c^Tx\]
\[Ax=b\]
\[x \ge 0\]
\[Where ~~ A \in R^{m \times n},~Rank(A)=m\]
with the corresponding symmetric dual problem,
\[\underset{y}{\operatorname{max}} ~ b^Ty\]
\[A^Ty \le c\]
\[Where ~~ A \in R^{m \times n},~Rank(A)=m\]
 \end{document}
